VIPRE: Virtualized Intermittently-Powered Runtime Environment

### 2017-07-06 paper/paper.tex
ACM conference-required information added to the paper

@@

\title{VIPRE: Virtualized Intermittently-Powered Runtime Environment}

%Amjad Yousef Majid, Kas{\i}m Sinan Y{\i}ld{\i}r{\i}m, Przemys{\l}aw Pawe{\l}czak,
%TU Delft, Mekelweg\,4, 2628\,CD Delft, NL
%\{a.y.majid, k.s.yildirim, p.pawelczak\}@tudelft.nl
%
%Kiwan Maeng, Alexei Collin, Brandon Lucia
%Carnegie Mellon University, 4720 Forbes Avenue, Pittsburgh, PA 15213, USA
%\{kmaeng, acolin, blucia\}@kmaeng@andrew.cmu.edu

@@

>>>>

\setcopyright{rightsretained}

\acmDOI{http://dx.doi.org/xx.xxxx/xxxxxxx.xxxxxxx}

\acmISBN{978-1-xxxx-xxxx-x/17/11}

\acmConference[ASPLOS]{The 23rd ACM International Conference on Architectural Support for Programming Languages and Operating Systems}{March 24--28, 2017}{Williamsburg, VA, USA}

\acmYear{2017}

\copyrightyear{2017}

\acmPrice{15.00}

@@

\title[VIPRE: Virtualized Intermittently-Powered Runtime Environment]{VIPRE: Virtualized Intermittently-Powered Runtime Environment}

%Note: order of authors placed randomly

\author{Kiwan Maeng}
%\authornote{}
%\orcid{}
\affiliation{%
	\institution{Carnegie Mellon University}
	\streetaddress{4720 Forbes Avenue}
	\city{Pittsburgh} 
	\state{PA} 
	\postcode{15213}
}
\email{kmaeng@andrew.cmu.edu}

\author{Alexei Colin}
%\authornote{}
%\orcid{}
\affiliation{%
	\institution{Carnegie Mellon University}
	\streetaddress{4720 Forbes Avenue}
	\city{Pittsburgh} 
	\state{PA} 
	\postcode{15213}
}
\email{acolin@andrew.cmu.edu}

\author{Brandon Lucia}
%\authornote{}
%\orcid{}
\affiliation{%
	\institution{Carnegie Mellon University}
	\streetaddress{4720 Forbes Avenue}
	\city{Pittsburgh} 
	\state{PA} 
	\postcode{15213}
}
\email{blucia@andrew.cmu.edu}

\author{Amjad Yousef Majid}
%\authornote{}
%\orcid{}
\affiliation{%
	\institution{Delft University of Technology}
	\streetaddress{Mekelweg 4}
	\city{Delft, The Netherlands} 
	\state{Zuid Holland} 
	\postcode{2628\,CD}
}
\email{a.y.majid@tudelft.nl}

\author{Kas{\i}m Sinan Y{\i}ld{\i}r{\i}m}
%\authornote{}
%\orcid{}
\affiliation{%
	\institution{Delft University of Technology}
	\streetaddress{Mekelweg 4}
	\city{Delft, The Netherlands} 
	\state{Zuid Holland} 
	\postcode{2628\,CD}
}
\email{k.s.yildirim@tudelft.nl}

\author{Przemys{\l}aw Pawe{\l}czak}
%\authornote{}
%\orcid{}
\affiliation{%
	\institution{Delft University of Technology}
	\streetaddress{Mekelweg 4}
	\city{Delft, The Netherlands} 
	\state{Zuid Holland} 
	\postcode{2628\,CD}
}
\email{p.pawelczak@tudelft.nl}

\renewcommand{\shortauthors}{A. Y. Majid et al.}

@@

% The code below should be generated by the tool at 
%http://dl.acm.org/ccs.cfm Please copy and paste the code instead of the 
%example below.

\begin{CCSXML}
	<ccs2012>
	<concept>
	<concept_id>10010520.10010553.10010562.10010564</concept_id>
	<concept_desc>Computer systems organization~Embedded 
	software</concept_desc>
	<concept_significance>500</concept_significance>
	</concept>
	<concept>
	<concept_id>10010520.10010575.10010578</concept_id>
	<concept_desc>Computer systems organization~Availability</concept_desc>
	<concept_significance>300</concept_significance>
	</concept>
	<concept>
	<concept_id>10011007.10010940.10010941.10010949.10010957.10010688</concept_id>
	<concept_desc>Software and its engineering~Scheduling</concept_desc>
	<concept_significance>300</concept_significance>
	</concept>
	<concept>
	<concept_id>10011007.10010940.10010941.10010949.10010965</concept_id>
	<concept_desc>Software and its engineering~Communications 
	management</concept_desc>
	<concept_significance>300</concept_significance>
	</concept>
	<concept>
	<concept_id>10011007.10010940.10010971.10010564</concept_id>
	<concept_desc>Software and its engineering~Embedded 
	software</concept_desc>
	<concept_significance>300</concept_significance>
	</concept>
	</ccs2012>
\end{CCSXML}

\ccsdesc[500]{Computer systems organization~Embedded software}
\ccsdesc[300]{Computer systems organization~Availability}
\ccsdesc[300]{Software and its engineering~Scheduling}
\ccsdesc[300]{Software and its engineering~Communications management}
\ccsdesc[300]{Software and its engineering~Embedded software}

\keywords{Energy harvesting, transient operation, operating system}
